6.829 Final Project: A comparison of bit rate selection algorithms

### 2013-05-17 paper/paper.tex
fixed typo

Minstrel and SampleRate perform similarly.  The results suggest that
SampleRate tends to perform slightly better, except in very lossy
links such as the client being far awat from the AP or actively
moving.  Minproved, our improved version of Minstrel, solidly
outperforms both Minstrel and SampleRate.

It seems that the replacement of SampleRate in the Linux kernel may
have been a hasty, since it seems to perform similarly to Minstrel and
it is a much simpler algorithm and thus simpler to adapt to changing
wireless standards.  We are not sure if adjustments to SampleRate can
bring its performance to match that of Minproved, however.

>>>>

Minstrel and SampleRate perform similarly.  The results suggest that
SampleRate tends to perform better, except in very lossy
links such as the client being far away from the AP or actively
moving.  Minproved, our improved version of Minstrel, solidly
outperforms both Minstrel and SampleRate.

It seems that the replacement of SampleRate in the Linux kernel may
have been a hasty, since it performs similarly or better than Minstrel 
and in most situations and is a much simpler algorithm, and thus simpler
 to adapt to changing wireless standards.  We are not sure if 
adjustments to SampleRate can bring its performance to match that of 
Minproved, however.
